Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-11 syntaxsemantics.tex
+

   Definition load (w: { w: word 64 | aligned w }):word 64 + MemFail :=

@@

  Definition store (w: { w: word 64 | aligned w }) (v: word 64):mem64 * (unit + MemFail) :=

>>>>

   Definition load (w:{w: word 64 | aligned w}):word 64 + MemFail :=

@@

  Definition store (w:{w: word 64 | aligned w}) (v:word 64):mem64 * (unit + MemFail) :=
